---
title       : Análise de dados 
subtitle    : Módulo básico
author      : Marcio Nicolau
job         : Estatístico
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft, selfcontained}
ext_widgets : {rCharts: [libraries/nvd3, libraries/highcharts]}
github      : {user: marcionicolau, repo: courses}
assets:
  css: 
    - "http://fonts.googleapis.com/css?family=Open+Sans"
    - "http://fonts.googleapis.com/css?family=Oxygen"
--- &radio
<style>

body{
  font-family: 'Open Sans', sans-serif;
  font-size: 16px;
  line-height: 24px;
}

h1,h2,h3,h4 {
  font-family: 'Oxygen', sans-serif;
}

.container { width: 900px; }
</style>


## Question 1

What is 1 + 1?

1. 1
2. _2_
3. 3
4. 4

*** .hint

This is a hint

*** .explanation

This is an explanation

---
## Interactive Chart
```{r echo = FALSE, results = 'asis'}
require(rCharts)
haireye = as.data.frame(HairEyeColor)
n1 <- nPlot(Freq ~ Hair, group = 'Eye', type = 'multiBarChart',
  data = subset(haireye, Sex == 'Male')
)
n1$print('chart1')
```

--- &interactive
## Interactive Console

```{r opts.label = 'interactive', results = 'asis'}
require(googleVis)
M1 <- gvisMotionChart(Fruits, idvar = 'Fruit', timevar = 'Year')
print(M1, tag = 'chart')
```


---
## Interactive 2
```{r opts.label = 'shiny'}
slidifyUI(
  sidebarPanel(
    selectInput('sex', 'Choose Sex', c('Male', 'Female')),
    selectInput('type', 'Choose Type',
      c('multiBarChart', 'multiBarHorizontalChart')
    )
  ),
  mainPanel(
    tags$div(id = 'nvd3plot', class='shiny-html-output nvd3 rChart')
  )
)
```

---
## Interactive 3
```{r echo = FALSE, results = 'asis'}
require(rCharts)
r1 <- rPlot(mpg ~ wt | am + vs, 
  data = mtcars, 
  color = 'gear',
  type = 'point'
)
r1$addControls("x", "wt", names(mtcars))
r1$addControls("y", "mpg", names(mtcars))
r1
```

--- &twocols
### Two Column Layout   
This slide has two columns
    
*** =left w:40%
    
- point 1
- point 2
- point 3
    
*** =right w:60%

- point 1
- point 2
- point 3

--- &twocols

### Two Columns

This slide has two columns

*** =left w:60%

- point a
- point b
- point c

*** =right w:40%

- point a
- point b
- point c

---

## Another attempt to add rCharts

```{r echo = T}
haireye = as.data.frame(HairEyeColor)
n1 <- nPlot(Freq ~ Hair, group = 'Eye', type = 'multiBarChart',
  data = subset(haireye, Sex == 'Male')
)
n1$addParams(width = 500, height = 500)
n1$addControls("group", "Eye",names(haireye))
n1$addControls("type", "multiBarChart", c('multiBarChart', 'multiBarHorizontalChart'))
n1$save("rp2.html", cdn=TRUE)
```
<iframe src="rp2.html" width=1200 height=600> </iframe>

